SPARQL on the Open, Decentralised Web

### 2016-06-25 dissertation/related.tex
improve description of Dividino shorten and ease the critisism

Dividino et al. \cite{Dividino2015} proposed strategies to keep caches
of Linked Open Data up to date, in face of changing data. The authors
sets out to learn the change frequency of resources, and based on that
schedule updates of the resources. This does then not depend on the
resource metadata (neither HTTP headers nor metadata in the RDF
itself, which I studied in \cite{kjernsmo_survey_2015}), which is
motivated by their finding that only 8\% of \httph{Last-Modified}
headers they surveyed reflected the true change frequency. While I
have no reason to doubt this finding, and the monitoring approach is
interesting, I think the dismissal of resource metadata is
insufficiently motivated, and therefore the evaluation is
inadequate. First, the \httph{Last-Modified} header is far from the
only cache-relevant header, as should be evident by the fact that it
is not defined in the cache standard, RFC7234, but in the conditional
request standard, RFC7232. Moreover, RFC7234 contains a Section~4.2.2
titled ``Calculating Heuristic Freshness''. It is my opinion that the
paper should be framed within the loose constraints of this section,
where it could make a substantial contribution. As it stands, it would
serve to violate Web standards, which in my opinion, is something the
Semantic Web community should be more cautious about. RFC7234's
Section~4.2.2 also proposes a simple heuristic for calculating
freshness lifetime. I found that the distribution of this heuristic
freshness lifetime agrees well with The Dynamic Linked Data
Observatory (DyLDO) \cite{dyldo2}. However, a weakness of my study
which could make this observation irrelevant, is that I considered
only summary statistics. If the change frequency of individual
resources were wrong, in particular, if the use of the simple
heuristic lead to using stale content, it would be inappropriate to
use the simple heuristic.  RFC7234's explicitly prohibits the use of a
heuristic if an explicit expiration time is present, yet the paper
does not attempt to include those in their assessment. Furthermore, I
found in \cite{kjernsmo_survey_2015} that cache prohibitions were
common. While they in many cases may be misguided, they nevertheless
express a strong statement from the server administrators, that should
be respected. RDF data, e.g. \rdfterm{dct:valid} and
\rdfterm{dct:modified} could also be used to compute a expiration
time. Finally, an opaque validator, \httph{ETag} is also a part of
RFC7232. After considering cache prohibitions, explicit expiration
times, opaque validators, simpler heuristics, etc., the space where
learning the change frequency could be applied is likely much
smaller. However, if understood as a sophisticated heuristic within
the constraints of RFC7234's Section~4.2.2, the contribution is
valuable.

>>>>

Dividino et al. \cite{Dividino2015} proposed strategies to keep caches
of Linked Open Data up to date, in face of changing data. The authors
set out to learn the change frequency of resources representations,
and based on that schedule updates of them as efficiently as possible
under bandwidth constraints. Instead of relying on resource metadata,
the authors propose an algorithm that iteratively ensures the quality
of the cache by examining the resource representations that have been
downloaded and compute certain metrics, such a dynamicity and
changerate.

While the approach is interesting and useful, I nevertheless have some
points of critisism: They motivate their approach from an earlier
finding that only 8\% of \httph{Last-Modified} headers they surveyed
reflected the true change frequency. While I have no reason to doubt
this finding, the authors boldly go on to claim that `` The only
alternative [to \httph{Last-Modified}] is to actually retrieve the
data from the sources and check it for changes.'', but this
contradicts the results I found in \cite{kjernsmo_survey_2015}. The
authors have not considered all alternatives, including not the
alternative presented by the HTTP caching standard RFC7234 discussed
in Section~\ref{sec:httpcache}, which invalidates that
assertion. Moreover, the author's approach would violate RFC7234 in
the case where their algorithm caches results that should not be
cached or has an explicit freshness lifetime, as discussed in
Section~\ref{sec:httpcache}. As a general observation, it is my belief
that the Semantic Web community should be more cautious about
violating core Web standards.
